---
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
library(here)

knitr::opts_chunk$set(echo = TRUE)
```


# superheroR

[Edgar Zamora | Twitter: `@Edgar_Zamora_`](https://twitter.com/Edgar_Zamora_)

```{r unsplash, echo=FALSE, fig.align='center', out.width="90%", fig.cap='Photo by <a href="https://unsplash.com/@waldemarbrandt67w?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">Waldemar Brandt</a> on <a href="https://unsplash.com/s/photos/comics?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">Unsplash</a>'}

include_graphics("https://images.unsplash.com/photo-1588497859490-85d1c17db96d?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1050&q=80")
  
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<br>

The `superheroR` package is a R wrapper that is used to request data from the [SuperHero API](https://superheroapi.com) by specific superhero. The API provides data about a superheros stats, biography, appearances, and more from over 500 superheros from both the comic universes. The only requirement is a access token which can be obtained by linking an individuals personal Facebook account.

# Setting access token

```{r access_token}

Sys.setenv(SUPERHERO_TOKEN = "xxxxxxxxxxxxxxx")

```


# Installation

```{r installation, eval=FALSE}
## install.packages(devtools)

devtools::install_github("Edgar-Zamora/superheroR")

```




# Credits






